---
title: "EDA with ggplot2"
author: "Qu Mengyuan"
date: "10/6/2019"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(bizdays)
library(dplyr)
# Use echo = TRUE for assignment is an exception, so code is visible.
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```
# Finding 1
Telemarketing is in highly active state during May and August and extremely active in May while in March, September, Octorber and December it is reletively dormant.
```{r}
# Find the distribution of last contact month
bank %>% 
  mutate(month_n = month(parse_date_time(month, "b"))) %>% 
  group_by(month_n) %>%
  summarise(count = n()) -> res
res
ggplot(res, aes(month_n, count)) + geom_col()
  
```

# Finding 2
Client's average yearly balance doen't has direct relationship with their age. 

At the begining of their career, they tend to have a relatively lower balance.
```{r}
# Find the relationship between age and balance.
ggplot(data = bank) +
  geom_point(mapping = aes(x = age, y = balance, color = job),alpha = 0.5) +
  facet_wrap( ~ job,nrow = 4)
```

# Finding 3
Generally, the higher education a client gets, the stronger willing he has to keep single. 

In other words, less education one gets, higher probability he/she is married.
```{r}
# Find the relationship between marital and education.
ggplot() +
  geom_bar(data = bank, mapping = aes(x = education, fill = marital))
```

# Finding 4
Generally, the higher **education** a client gets, the higher average yearly **balance** he has.

The average yearly balance among clients who have primary education _polarizes_.
```{r}
# Find the relationship between balance and education
ggplot(bank) +
  geom_boxplot(mapping = aes(x = education, y = balance))
```

# Finding 5
The number of people divorced in 30s,40s and 50s are similar but the single number of the single decreases with age increasing.

Most of people in 20s are single but while almost all clients over 60 years old are married.

```{r}
# Find the relationship between age and marital
bank <- mutate(bank,age_group = (age %/% 10) * 10)
bank %>% 
  dplyr::filter(marital=="married")  %>%
  group_by(age_group) %>%
  summarise(num = n()) -> res1
bank %>%
group_by(age_group) %>%
summarise(total = n()) -> res2
res <- full_join(res1,res2,by = "age_group")
res <- mutate(res, `marriage rate` = num/total)
res
ggplot() +
  geom_bar(data = bank, mapping = aes(x = age_group, fill = marital))
```

# Finding 6
The education level varies among jobs(excluding students and unknown).

The **managers** has the *highest* education leve, more than 75% of which has tertiary education.

The **housemaids** has the **lowest** education leve, nearly half of whom only get primary education.
```{r}
# Find the relationship between job and education
bank %>%
group_by(job,education) %>%
summarise(num = n()) %>%
  spread(education, num) -> res
res
ggplot() +
  geom_bar(data = bank, mapping = aes(x = job, fill = education),position = "fill") +
  scale_x_discrete(limit = rev(levels(bank$job))) + 
  coord_flip() 
```

# Finding 7
People who have personal loan have only around 55% of balance than those who don't have personal loan.
Housing loan has slight bad effects on people's balance condition.
People prefer not owning liabilities
```{r}
# Find the relationship between balance and loans
bank %>%
group_by(housing,loan) %>%
  summarise(average = mean(balance), median = median(balance)) -> res
res
library(scatterplot3d)
with(bank,{scatterplot3d(x = loan, y = housing, z = balance)})

ggplot(data = bank) +
  geom_point(mapping = aes(x = age, y = balance)) +
  facet_wrap(loan ~ housing, nrow = 2)
```

# Finding 8
People who don't have credit in default are in a **much better** balance condition compared with those who have credit in default, but have huge variation.
```{r}
# Find the relationship between default and balance
bank %>%
group_by(default) %>%
summarise(average = mean(balance), max = max(balance), min = min(balance), median = median(balance)) -> res
res
ggplot(bank, aes(default, balance)) + 
  geom_boxplot()
```

# Finding 9
The most common type of contact communication is by cellular.

The last contact durations of all three types concentrates around 175 seconds.

Generally, the last durations by *cellular* is the **longest** while that by *telephone* is the **shortest**.
```{r}
# Find the relationship between contact type and duration
bank %>%
group_by(contact) %>%
summarise(num = n(),average = mean(duration), max = max(duration), min = min(duration), median = median(duration)) -> res
res
ggplot(bank, aes(duration)) + geom_density(aes(fill = contact), alpha = 0.7) 
```

# Finding 10
In the previous marketing campaign，most of people gets secondory and tertiary education.

Generally, the **higher** educaion one gets, telemarketing has the **higher** possibility to success and **lower** possibility to fail, though *not significantly*.
```{r}
# outcome of the previous marketing campaign
bank %>%
  group_by(education, poutcome) %>%
  summarise(num = n()) %>%
  spread(poutcome, num)-> res
res
ggplot() +
  geom_bar(data = dplyr::filter(bank, poutcome !="unknown"), mapping = aes(x = education, fill = poutcome),position = "fill")
```
