---
title: "10 Findings"
author: "Zhou Xueming"
date: "December 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(bizdays)
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse=TRUE, cache=TRUE)
library(readr)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

## R Markdown

# Finding #1
relationship between marital status and education
```{r Finding1, echo = TRUE}
ggplot(bank) + geom_bar(mapping = aes(x=education, fill = marital), position = "fill") + coord_flip()
```

#Finding 2
Relationship between education and default:
There's no obvious relationship between education level and default.But we can see from the plot that default risk may be larger in 
younger groups.
```{r finding2, echo=TRUE}
ggplot(bank, aes(x = age, y = default, color = education)) +
geom_point() +theme(legend.position="right")
```

#Finding 3
relationship between loan status and age.
we can see that more younger people are under loan while people above 60 generally under no loan. 
```{r finding3, echo=TRUE}
ggplot(bank)+geom_histogram(mapping=aes(x=age,fill=loan), position="dodge")
```

#Finding 4
relationship between balance and age, grouped by housing status and education level.
we can see that primary eudcation with housing group has lowest balance.
```{r finding4, echo=TRUE}
ggplot(data = bank) +
geom_point(mapping = aes(age,balance)) +
facet_wrap(education ~ housing, nrow = 1)
```

#Finding 5
Relationship between defaul and age
```{r finding5, echo=TRUE}
ggplot(bank, aes(age, default)) + geom_point()
```

#Finding 6
Relationship between marital and age
```{r finding6, echo=TRUE}
ggplot(bank, aes(age, marital)) + geom_point()
```

#Finding 7
```{r finding7, echo=TRUE}
ggplot(bank, mapping = aes(x = job, fill = housing)) +
geom_bar() + coord_flip()+
ggtitle("housing vs job")
```

#Finding 8
duration according to age and contact
Telephone group has shorter duration compared to other groups.
```{r finding8, echo=TRUE}
ggplot(bank) + geom_point(aes(age, duration, color = contact))
```



#Finding 9
Relationship between housing and balance
```{r finding9, echo=TRUE}
ggplot(bank, aes(age,balance)) +
  geom_bar(aes(fill = housing), stat = "identity") +
  ggtitle("housing vs balance")
```

#Finding 10
marital status in different kind of jobs
```{r finding10, echo=TRUE}
ggplot(data = bank, mapping=aes(x=reorder(job, age, FUN=mean), fill=marital))+
  geom_bar()+coord_flip()
```











