---
title: "Assignment 3"
output: html_document
---

## Exploratory Data Work on Bank Dataset

In this markdown document, I am going to analyze the Bank dataset and get insights about the data



```{r, include=FALSE}
library(tidyverse)
library(lubridate)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```
<br>

#### 1. Distribution across Marital Status

Listed below is the distribution of people by their marital status 

<div class = "one">
```{r one}
b1<-bank %>%
  group_by(`marital`) %>%
  summarize(count = n())
for(i in 1:nrow(b1))
{
  cat(paste0("There are ",b1$count[i]," ",b1$marital[i],"\n"))
}
```
</div>

</br>

#### 2. Average Balance of Students

Listed below is the average balance of people whose job is listed as student 

<div class = "two">
```{r two}
bank %>%
  filter(job == "student") %>%
  summarize(Student_mean_balance = mean(balance))

```
</div>

</br>

#### 3. Housing and Loan Relation

Here I have summarised the distribution between possible subsets of housing and loan.

<div class = "three">
```{r three}
bank %>%
  group_by(housing,loan) %>%
  summarise(Percent=n()*100 / nrow(bank))
```
</div>


</br>

#### 4. Summary of balances

Here I have summarised the data of Balances column.

<div class = "four">
```{r four}
summary(bank$balance)
```
</div>

</br>

#### 5. Data across various Age Groups

Here we are finding distribution of data across age groups.

<div class = "five">
```{r five}
bank %>%
 group_by(age_group = (age %/% 25) * 25) %>%
 summarise(count = n()) %>%
 arrange(age_group) -> res
for (i in 1:nrow(res))
{
  cat(paste0("There are ",res$count[i]," customers between ",res$age_group[i]," to ",(res$age_group[i]+25)," \n"))
}
```
</div>

</br>

#### 6. Ratio of Customers with unknown contact

Here I am finding percent of customers who have unknown contact.

<div class = "six">
```{r six}
bank %>%
  filter(contact=="unknown") %>%
  group_by(contact) %>%
  summarise(percent = n()*100 / nrow(bank)) -> res
cat(paste0(round(res$percent[1],2),"% of customers have unknown contact.\n"))
```
</div>

</br>

#### 7. Distribution of poutcome

Here I am finding distribution of poutcome column.

<div class = "seven">
```{r seven}
bank %>%
  group_by(poutcome) %>%
  summarise(Percent=n()*100 / nrow(bank))
```
</div>

</br>

#### 8. Summarize balance of customers with loan=yes

Here I am finding the summary of balances of those customers whose loan=yes.

<div class = "eight">
```{r eight}
bank1<-bank %>%
  filter(loan=="yes")
summary(bank1$balance)
```
</div>

</br>

#### 9. Ratio of people with housing across different Education

Here I am finding distribution of people who have housing across different education background.

<div class = "nine">
```{r nine}
count_h<-nrow(bank %>%filter(housing=="yes"))
bank %>%
  filter(housing=="yes") %>%
  group_by(education) %>%
  summarise(percent= n()*100 / count_h)
```
</div>

</br>

#### 10. Possible states when binding columns loan and poutcome

Here I was finding possible pairs when binding columns loan and poutcome.

<div class = "ten">
```{r ten}
bank %>%
  select(loan,poutcome) %>%
  group_by(loan,poutcome) %>%
  summarise(percent = n()*100 / nrow(bank))
```
</div>

</br>
</br>
<style>
div.one pre { background-color:white; }
div.one pre.r { background-color:lightblue; }
div.two pre { background-color:white; }
div.two pre.r { background-color:lightblue; }
div.three pre { background-color:white; }
div.three pre.r { background-color:lightblue; }
div.four pre { background-color:white; }
div.four pre.r { background-color:lightblue; }
div.five pre { background-color:white; }
div.five pre.r { background-color:lightblue; }
div.six pre { background-color:white; }
div.six pre.r { background-color:lightblue; }
div.seven pre { background-color:white; }
div.seven pre.r { background-color:lightblue; }
div.eight pre { background-color:white; }
div.eight pre.r { background-color:lightblue; }
div.nine pre { background-color:white; }
div.nine pre.r { background-color:lightblue; }
div.ten pre { background-color:white; }
div.ten pre.r { background-color:lightblue; }

</style>
