---
title: "10 Findings"
author: "Kanawut Laoritthikrai"
date: "December 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(bizdays)
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse=TRUE, cache=T)
library(readr)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

## R Markdown



#Finding 1

Relationship between defaul and age

We can see that people who default are the age between 10 and 60.

```{r finding1, echo=TRUE}
ggplot(bank, aes(age, default)) + geom_point()

```



#Finding 2

Relationship between marital and age

```{r finding2, echo=TRUE}
ggplot(bank, aes(age, marital)) + geom_point()
```


#Finding 3

```{r finding3, echo=TRUE}
ggplot(bank, mapping = aes(x = job, fill = housing)) +
geom_bar() + coord_flip()+
ggtitle("housing vs job")

```




#Finding 4

Relationship between education and default:

Results show that the customers who default have a good mix of educational backgrounds. However, all of those who default are below 60 years old. 

```{r finding4, echo=TRUE}
ggplot(bank, aes(x = age, y = default, color = education)) +
geom_point() +theme(legend.position="right")
```

?aes



#Finding 5

Different duration depending on age and by contact group

Telephone using group has shorter duration compared to cellular using group and unknown group.

```{r finding5, echo=TRUE}
ggplot(bank) + geom_point(aes(age, duration, color = contact))
  

```



#Finding 6

Relationship between housing and balance

```{r finding6, echo=TRUE}
ggplot(bank, aes(age,balance)) +
  geom_bar(aes(fill = housing), stat = "identity") +
  ggtitle("housing vs balance")

```




#Finding 7

marital status in different kind of jobs

```{r finding7, echo=TRUE}
ggplot(data = bank, mapping=aes(x=reorder(job, age, FUN=mean), fill=marital))+
  geom_bar()+coord_flip()
```




#Finding 8

Elder people tend to get lower education but Youngster people receive higher education.
```{r finding8, echo=TRUE}
ggplot(bank) +
geom_bar(mapping = aes(x = age, fill = education), position = "fill") +
coord_polar()
```



#Finding 9

Count people in each age groups who have loan and haven't loan

We can see that elder people (age more than 60) don't have loan

```{r finding9, echo=TRUE}
ggplot(bank)+geom_histogram(mapping=aes(x=age,fill=loan), position="dodge")
```





#Finding 10

Plot of balance depending on age, grouped by housing and education

primary eudcation with housing group has lowest balance, compared to other groups.

```{r finding10, echo=TRUE}
ggplot(data = bank) +
geom_point(mapping = aes(age,balance)) +
facet_wrap(education ~ housing, nrow = 1)
```

