---
title: "Assignment3_first question"
author: "Zhu Yiqing"
date: "2020/10/9"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(bizdays)
library(ggplot2)
# Use echo = TRUE for assignment is an exception, so code is visible.
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
# bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

# Finding #1
This data contains `r nrow(data)` rows.
```{r}
rows <- nrow(bank)
print (rows)
```
# Discover insights of data frame: bank. 1st: age group
```{r}
# Find the big age group
bank %>%
group_by(age_group = (age %/% 10) * 10) %>%
  summarise(count = n()) %>%
  arrange(age_group) -> res
res
ggplot(res, aes(age_group, count,fill=age_group)) +geom_bar(stat="identity") +
  xlab("Age Group") + ylab("Number of People") 
```
# Discover insights of data frame: bank. 2nd: employment
```{r}
# Find the employment situation
# We also want to find out how much is in balance for different jobs
bank %>%
group_by(job) %>%
  summarise(count = n(),avg_balance=mean(balance)) %>%
  arrange(avg_balance)-> res2
p=ggplot(res2,aes(job,avg_balance),color=job)+geom_bar(stat="identity")+
  scale_x_discrete(guide=guide_axis(n.dodge=1.5,check.overlap=TRUE,angle=60)) +
  xlab("Job") + ylab("Average Balance")
p
```
# Discover insights of data frame: bank. 3rd: marital and housing
```{r}
# Find the marital status and housing relation
bank %>%
group_by(marital, housing) %>%
  summarise(number = n()) %>%
  mutate(percentage = number/sum(number))-> res3
ggplot(res3,aes(marital,percentage,fill=housing))+
  geom_bar(stat="identity",position="stack")+
  theme(axis.ticks.length=unit(0.5,'cm'))

```
# Discover insights of data frame: bank. 4th: duration
```{r}
# Find the duration's distribution
bank %>%
group_by(duration_group = (duration %/% 20) * 20) %>%
  summarise(count = n()) %>%
  arrange(duration_group) -> res4
ggplot(res4, aes(duration_group, count)) + geom_point() +
  xlab("Duration") + ylab("Number of People")
```
# Discover insights of data frame: bank. 5th: month
```{r}
# Find month's distribution
mon_order <- data.frame(month = c("jan", "feb", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"))
bank %>%
  group_by(month) %>%
  summarise(number = n()) -> res5_tempt
# res6 <- res5[order(factor(res5$month, levels = mon_order)),]
res5 <- left_join(mon_order,res5_tempt,by="month")
res5
res5$month <- factor(res5$month, levels = res5$month)
p=ggplot(res5,aes(month, number),color=month)+geom_bar(stat="identity")+
  scale_x_discrete(guide=guide_axis(n.dodge=1.5,check.overlap=TRUE,angle=60)) +
  xlab("Month") + ylab("Number of People")
p
```
# Discover insights of data frame: bank. 6th: education
```{r}
# We also want to find out how much is in balance for different jobs
bank %>%
group_by(education) %>%
  summarise(count = n(),avg_balance=mean(balance)) %>%
  arrange(avg_balance)-> res6
p=ggplot(res6,aes(education,avg_balance),color=education)+geom_bar(stat="identity")+
  scale_x_discrete(guide=guide_axis(n.dodge=1.5,check.overlap=TRUE,angle=60)) +
  xlab("Education") + ylab("Average Balance")
p
```
# Discover insights of data frame: bank. 7th: contact
```{r}
bank %>%
  group_by(contact) %>%
  summarise(number = n()) %>%
  mutate(all = 'contact')-> res7
p=ggplot(res7,aes(all,number,fill=contact))+
  geom_bar(stat="identity",position="stack")+
  coord_polar("y", start=0)

p
```



