---
title: "Question2"
author: "Li Jiajing"
date: "2019/9/28"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse) 
library(lubridate) 
library(bizdays) 
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

# Finding #1
```{r age_housing}
age_housing <- group_by(bank,age) %>%
  summarise(n = n(),
            housing_ratio = sum(ifelse(default == "no", 0, 1))/n)
arrange(age_housing) -> finding1
finding1
ggplot(finding1, aes(age, housing_ratio)) +
  geom_point()
```

* Housing ratio of people around 20 and above 60 is 0.

* Housing ratio of people between 20 and 60 has no clear trend with respect to age increasing(approximately random).

# Finding #2
```{r age_balance}
age_balance <- group_by(bank,age) %>%
  summarise(n = n(),
            balance = mean(balance))
arrange(age_balance) -> finding2
finding2
finding2 <- as.data.frame(finding2)
ggplot(finding2, aes(age, balance)) +
  geom_point() + 
  geom_smooth(method = "loess", se = FALSE)
```

* Average balance of people above 60 fluctuates more violently than that of people below 60.

# Finding #3
```{r job_balance}
min <- group_by(bank, job) %>%
  summarise("min" = min(balance))
max <- group_by(bank, job) %>%
  summarise("max" = max(balance))
job_balance <- distinct(bank, job) %>% arrange(job)
job_balance <- left_join(job_balance, min, by = "job")
job_balance <- left_join(job_balance, max, by = "job")
job_balance <- mutate(job_balance, "range" = max - min)
arrange(job_balance) -> finding3
finding3
ggplot(bank, aes(job, balance)) + 
  geom_boxplot()
```

* Count the minimum, the maximum and the range of balance of each job.

* The highest maximum balance is from retired and the lowest minimum balance is from self-employed.

# Finding #4
```{r job_education}
job_education <- group_by(bank,job) %>%
  summarise(n = n())
arrange(job_education) -> finding4
finding4
ggplot(bank) + 
  geom_bar(aes(x = job, stat = "count", fill = education))
```

* Most people in management are tertiary education.

* The proportion of primary education is significantly higher in blue-collar, housemaid and retired than in other jobs.

* Secondary education takes the largest proportion in people of job admin., blue-collar, retired, services, student, technician and unemployed.

# Finding #5
```{r duration_pdays}
duration_pdays <- group_by(bank,contact) %>%
  summarise(n = n(),
            duration = mean(duration),
            pdays = mean(pdays))
arrange(duration_pdays) -> finding5
finding5
ggplot(bank) + 
  geom_point(aes(duration, pdays, color = contact))
```

* Cellular is the most used communication type.

* Ignore the 0 ones, the distribution of number of days that passed by after the client was last contacted from a previous campaign is approximately concentrated in the range of 62.5 to 375.

* People who have "pdays" more than 375 hardly take duration longer than 500 seconds.

# Finding #6
```{r job_marital}
job_marital <- group_by(bank,job) %>%
  summarise(n = n(),
            marital_ratio = sum(ifelse(marital == "married", 1, 0))/n) 
arrange(job_marital) -> finding6
finding6
ggplot(finding6, aes(job, marital_ratio)) +
  geom_point()
```

* Students have the lowest marital ratio (of course lol).

# Finding #7
```{r job_count}
job_count <- group_by(bank,job) %>%
  summarise(n = n())
arrange(job_count) -> finding7
finding7
ggplot(bank) +  
  geom_bar(aes(x = job)) 
```

* The job type which includes largest population is management.

* The job type which includes least population except for unknown is student.

# Finding #8
```{r balance_distribution}
balance_distribution <- group_by(bank,education) %>%
  summarise(n = n(),
            balance = mean(balance))
arrange(balance_distribution) -> finding8
finding8
ggplot(bank, aes(balance, color = education)) + 
  geom_density()
```

* The average balance of tertiary education people is the highest among all four educations.

* The shapes of the distribution of balance seem to be similar despite the different value of peaks among different educations.

# Finding #9
```{r month_count}
month_count <- group_by(bank, month) %>%
  summarise(n = n())
arrange(month_count) -> finding9
finding9
ggplot(bank) + 
  geom_bar(aes(x = month, fill = poutcome))
```

* May is the month which happens most last contacts, while December is the month which happens least last contacts.

* The most common contact result is "unknown".

* "Failure" happens more frequently or as frequently as "success" in each month.


# Finding #10
```{r job_loan}
job_loan <- group_by(bank, job) %>%
  summarise(n = n(),
            loan_ratio = sum(ifelse(loan == "yes", 1, 0))/n)
arrange(job_loan) -> finding10
finding10
ggplot(finding10, aes(job, loan_ratio)) +
  geom_point()
```

* Entrepreneurs are most likely to have personal loans, while students are least likely to have personal loans.



