---
title: "Group Assignment 1"
author: "Abhishek Vijaykumar,Gaurav Singh,Manav Mehra,Suman Gunda"
date: "December 17, 2018"
output:
  html_document: default
---

## 1.Setup for global configuration/libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 500)
library(tidyverse)
library(readxl)
library(ggplot2)
library(lubridate)
library(data.table)
library(randomNames)
library(kableExtra)

# setwd("C:\\Users\\singh\\Desktop\\syllabus\\Mini 3\\FE8828 Programming Web Applications in Finance (E)\\Homework_Assignments\\FE8828-Gaurav_Singh\\Group_Assignment\\")
setwd("E:\\gdrive\\MFECourse\\FE8828\\2018\\FE8828-Gaurav_Singh\\Group_Assignment")
```


## 2.Random Account Numbers and Names
```{r df1 AccNum and Name}
startDateOrig<-as.Date("2018-07-01")
endDateOrig<-as.Date("2018-09-30")
startDate<-startDateOrig
endDate<-endDateOrig

#df1 Account num with names
names<-randomNames(10)
sampleSize<-10
accountNums<-sample(100000:100999,sampleSize,replace=FALSE)
df1<-data.frame("AccountNo"=accountNums,"Name"=names)
kable(df1) %>% kable_styling(bootstrap_options = c("striped","hover"))
```

## 3.Making Empty Data Frame for Transactions

```{r df2 Transactions}
df2 <- data.frame(matrix(ncol = 6, nrow = 0))
colnames(df2) <- c("TransactionNo","Date","AccountNo","TransactionType","Amount","Currency")
kable(df2) %>% kable_styling(bootstrap_options = c("striped","hover"))
```

## 4.Making Data Frame for Currency Conversion With Values adjusted for missing days by taking the last known value
## Data from the internet stored in excel file and imported

```{r df3 currency conversion,echo=FALSE,message=FALSE}
#df3 Conversion Rate
SGDbyCNY <- read.csv(file="SGD_CNY Historical Data.csv", header=TRUE, sep=",")
colnames(SGDbyCNY)<- c("Date","Price","Open" ,"High","Low","Change")
SGDbyCNY$Date<-as.Date(SGDbyCNY$Date,format= "%B %d, %Y")
SGDbyCNY<-SGDbyCNY[,c(1,2)]
tempDateVec<-data.frame("Date"=seq(startDate, endDate, by="day"))
tempDateVec<-data.frame("Date"=anti_join(tempDateVec,data.frame("Date"=SGDbyCNY[,1])))
SGDbyCNY <-full_join(SGDbyCNY,tempDateVec,by="Date")
SGDbyCNY<- SGDbyCNY[order(SGDbyCNY$Date),]
SGDbyCNY<- cbind(SGDbyCNY,shift(SGDbyCNY$Price,1))
colnames(SGDbyCNY)<-c("Date","Price","Currency")
SGDbyCNY$Price[is.na(SGDbyCNY$Price)] <- SGDbyCNY$Currency[is.na(SGDbyCNY$Price)]
SGDbyCNY$Currency<-rep("CNY",endDate-startDate+1)

SGDbyUSD <- read.csv(file="SGD_USD Historical Data.csv", header=TRUE, sep=",")
colnames(SGDbyUSD)<- c("Date","Price","Open" ,"High","Low","Change")
SGDbyUSD$Date<-as.Date(SGDbyUSD$Date,format= "%B %d, %Y")
SGDbyUSD<-SGDbyUSD[,c(1,2)]
tempDateVec<-data.frame("Date"=seq(startDate, endDate, by="day"))
tempDateVec<-data.frame("Date"=anti_join(tempDateVec,data.frame("Date"=SGDbyUSD[,1])))
SGDbyUSD <-full_join(SGDbyUSD,tempDateVec,by="Date")
SGDbyUSD<- SGDbyUSD[order(SGDbyUSD$Date),]
SGDbyUSD<- cbind(SGDbyUSD,shift(SGDbyUSD$Price,1))
colnames(SGDbyUSD)<-c("Date","Price","Currency")
SGDbyUSD$Price[is.na(SGDbyUSD$Price)] <- SGDbyUSD$Currency[is.na(SGDbyUSD$Price)]
SGDbyUSD$Currency<-rep("USD",endDate-startDate+1)

SGDbySGD<-data.frame("Date"=seq(as.Date("2018-07-01"), as.Date("2018-09-30"), by="day"),"Price"=1,"Currency"="SGD")

df3 <- rbind(SGDbyCNY[,c(3,2,1)],SGDbyUSD[,c(3,2,1)],SGDbySGD[,c(3,2,1)])
colnames(df3)<-c("Currency","Conversion","Date")
paste("Sample Currency Concersion Table \n")
kable(df3[5,]) %>% kable_styling(bootstrap_options = c("striped","hover"))
#df3 <- mutate(df3,"EquivalentSGD")
#----------------------------------
```

## 5.Seeding initial balance

```{r df4 Seeding initial balance}
df4 <- data.frame("AccountNo"=accountNums,"DepositBalance"=sample(5000:10000,sampleSize),"CreditBalance"=sample(5000:10000,sampleSize))
kable(df4) %>% kable_styling(bootstrap_options = c("striped","hover"))

```


## 6.Seeding random Transactionsentries ( value to be added later )

```{r df5 Seeding random txns,echo=FALSE,message=FALSE}
txnNum<-2018001
#ledger starts
seedmoney<-data.frame(cbind(df4),"Date"=rep(startDateOrig,sampleSize),"TransactionType"=rep("Deposit",sampleSize),"Currency"=rep("SGD",sampleSize),"TransactionNo"=seq(txnNum,txnNum+sampleSize-1,by=1),"Amount"=rep(0,sampleSize))
seedmoney<-seedmoney[,c(7,4,1,5,8,6,2,3)]
txnNum<-txnNum+sampleSize
ledger<-merge(data.frame("Month"),merge(merge(df2,df3,by=c("Date","Currency")),df4,by="AccountNo"))
colnames(ledger)[1]<-"Month"
colnames(ledger)[9]<-"EquivalentSGD"
txnData<-data.frame("AccountNo"=character(),"Date"=character(),"TransactionType"=character())
for(k in 1:sampleSize)
{
  startDate<-startDateOrig
  endDate<-endDateOrig
  start_month<-month(as.POSIXlt(startDate, format="%d-%m-%Y"))
  end_month<-month(as.POSIXlt(endDate, format="%d-%m-%Y"))
  for(monthLoop in start_month:end_month)
  {
    numberOfDeposits<-sample(1:2,1)
    dateDeposit<-data.frame("Date"=sample(seq(startDate, startDate+months(1)-days(1), by="day"), numberOfDeposits), "TransactionType"="Deposit")
    numberOfSW<-sample(0:60,1)
    dateSW<-data.frame("Date"=sample(seq(startDate, startDate+months(1)-days(1), by="day"), numberOfSW,replace=TRUE),"TransactionType"=sample(c("Payment","Withdrawal"),numberOfSW,replace=TRUE))
    df_temp<-rbind(dateDeposit,dateSW)
    df_temp<-cbind("AccountNo"=rep(accountNums[k],nrow(df_temp)),df_temp[order(df_temp$Date),])
    txnData<-rbind(txnData,df_temp)
    startDate<-startDate+months(1)
  }
}

txnData<-cbind(txnData,"Currency"=sample(c("SGD","USD","CNY"),nrow(txnData),replace=TRUE),"TransactionNo"=seq(txnNum,txnNum+nrow(txnData)-1,by=1),"Amount"=rep(0,nrow(txnData)))
txnData<-cbind(txnData[,c(5,2,1,3,6,4)],"DepositBalance"=rep(0,nrow(txnData)),"CreditBalance"=rep(0,nrow(txnData)))
txnData<-cbind(rbind(seedmoney,txnData),"EquivalentSGD"=rep(0,nrow(rbind(seedmoney,txnData))))
txnData$EquivalentSGD<-txnData$EquivalentSGD
txnData<-merge(txnData,df3,by=c("Date","Currency"))
txnData<- txnData[order(txnData$TransactionNo),]
txnNum<-txnNum+nrow(txnData)
txnData$DepositBalance<-rep(0,nrow(txnData))

```


## 7.Seeding random Transactions values based on boundary conditions

```{r df6 Seeding random values,echo=FALSE,message=FALSE}
for(k in 11:nrow(txnData))
{
  if(txnData$TransactionType[k]=="Deposit")
  {
    txnData$Amount[k]<-sample(3000*txnData$Conversion[k]:5000*txnData$Conversion[k],1)/txnData$Conversion[k]/3000
    df4[which(df4$AccountNo == txnData$AccountNo[k]),2]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]+txnData$Amount[k]
    txnData$DepositBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]
    txnData$CreditBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),3]
    } 
  else if(txnData$TransactionType[k]=="Withdrawal")
  {
    txnData$Amount[k]<-(-1)*sample(0:df4[which(df4$AccountNo == txnData$AccountNo[k]),2]*txnData$Conversion[k],1)/txnData$Conversion[k]
    df4[which(df4$AccountNo == txnData$AccountNo[k]),2]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]+txnData$Amount[k]
    txnData$DepositBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]
    txnData$CreditBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),3]
  }
  else
  {
    txnData$Amount[k]<-(-1)*sample(0:(df4[which(df4$AccountNo == txnData$AccountNo[k]),2]+df4[which(df4$AccountNo == txnData$AccountNo[k]),3])*txnData$Conversion[k],1)/txnData$Conversion[k]
    if(-1*txnData$Amount[k]>df4[which(df4$AccountNo == txnData$AccountNo[k]),3])
    {
      df4[which(df4$AccountNo == txnData$AccountNo[k]),2]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]+txnData$Amount[k]+df4[which(df4$AccountNo == txnData$AccountNo[k]),3]
      df4[which(df4$AccountNo == txnData$AccountNo[k]),3]<-0
      txnData$DepositBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]
      txnData$CreditBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),3]
      }
    else
    {
      df4[which(df4$AccountNo == txnData$AccountNo[k]),3]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),3]+txnData$Amount[k]
      txnData$DepositBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),2]
      txnData$CreditBalance[k]<-df4[which(df4$AccountNo == txnData$AccountNo[k]),3]
      }
  }
}
txnData$Amount<-round(txnData$Amount*txnData$Conversion[k],2)
txnData$DepositBalance<-round(txnData$DepositBalance,2)
txnData$CreditBalance<-round(txnData$CreditBalance,2)
txnData<- txnData[order(txnData$TransactionNo),]
txnData <- txnData[txnData$Amount!=0, ] 
kable(txnData) %>% kable_styling(bootstrap_options = c("striped","hover"))

```

## 8.Month End Statement Customer-wise, Month-wise

```{r df7 Month End Statement Customer-wise, Month-wise}
#print(df1)
txnData2<-txnData[,c(1,4,3,5,6,2,7,8)]
for(i in 1:sampleSize)
{
  for(j in month(startDateOrig):month(endDateOrig))
  {
    paste(cat("Client Name : ",as.character(df1$Name[[which(df1$AccountNo == accountNums[i])]]),"\n"))
    paste(cat("Month : ",month.abb[j],"\n"))
    print(select(txnData2 %>% dplyr::filter((month(Date)==j)&(AccountNo==accountNums[i])),c(1,4,5,6,7,8)))
    print("Month-End Balance\n")
    print(txnData2 %>% dplyr::filter((month(Date)==j)&AccountNo==accountNums[i]) %>% summarise("TotalDeposit"=sum(DepositBalance),"TotalCredit"=sum(CreditBalance)))
    print("----------------------------")
  }
}
txnData2 %>% group_by(.,TransactionType) %>% summarise("Amount:"=sum(Amount))
```

## The dplyr usage helps us to achieve obtain insightful reports with less amount of coding effort as seen above.