---
title: "Week 3 Demo"
output: html_notebook
---

# Use mutate with functions.

## create a data frame
```{r}
bond_cf <- tibble(date = 1:10, cf = rep(1,10))
bond_cf <- mutate(bond_cf, cf = ifelse(date == 10, cf + 100, cf))
bond_cf <- mutate(bond_cf, dcf = exp( - 0.03 * date) * cf)
# older syntax if we don't use mutate
# bond_cf['dcf'] <- exp( -0.03 * bond_cf['date']) * bond_cf['cf']
```

## add new columns
```{r}
bond_cf <- mutate(bond_cf, dcf_diff_mean = dcf - mean(dcf))
bond_cf <- mutate(bond_cf, dcf_perc = dcf / sum(dcf))
bond_cf <- mutate(bond_cf, dcf_diff_next2 = dcf - lag(dcf,2))
```

## calculate MA
```{r}
bond_cf <- mutate(bond_cf, tcf = cumsum(dcf))

ma_n <- 5
bond_cf <- mutate(bond_cf,
    tcf_ma = tail((c(0,tcf) - lag(c(0,tcf),ma_n))/ma_n,-1))
```

We start from below expression which calculate MA.
# tcf : cumulative sum of dcf. 
tcf - lag(tcf,2)

Explain:

dcf:                       1, 2, 3, 4
tcf = cumsum(dcf):         1, 3, 6,10
lag(tcf, 2):              NA,NA, 1, 3
tcf - lag(tcf,2):         NA,NA, 5, 7
We expect MA to be        NA, 3, 5, 7  / 2
We just miss 3 in the front.

A: cumsum(padded):         0, 1, 3, 6, 10
B: cumsum(padded,lagged): NA,NA, 0, 1,  3, 6
A - B:                    NA,NA, 3, 5,  7
tail(A-B,-1):             NA ,3, 5, 7 / 2 
This is we expected to be the MA.

The whole express is below

tail(c(0,tcf) - lag(c(0,tcf),ma_n)) / ma_n, -1)


Hint:
# remove the first element
tail(1:10, -1)

# remove the last element
head(1:10, -1)


```{r}
bond_cf <- mutate(bond_cf, rr = rank(dcf))
bond_cf <- mutate(bond_cf, tt = ntile(dcf,2))
bond_cf <- mutate(bond_cf, nn = row_number())
```

## Environment

```{r}
x <- 3
local({
  print(x)
  assign("x",1,envir=.GlobalEnv)
  print(x)
})
print(x)

# We shall expect output of 3,1,3. x in the out environment is unchanged.


abc <- function() {
  x <- 3
  env <- environment()
  local({
    print(x)
    assign("x",1,envir=env)
    print(x)
  })
  print(x)
}

abc()

# We shall expect output of 3,1,1. x in the out environment is changed.
```

# Pipe

```{r}
# re-write them with pipe
bond_cf <- tibble(date = 1:10, cf = rep(1,10))

bond_cf2 <- bond_cf %>%
            mutate(cf = ifelse(date == 10, cf + 100, cf)) %>%
            mutate(dcf = exp( - 0.03 * date) * cf) %>% {
              v <- .
              print(v)
              mutate(v, new_col = "Y")
            } %>%
            mutate(x = dfc - mean(dcf)) %>%
            mutate(x = dcf / sum(dcf))

distinct(bank, job) %>% mutate(dummy = 1)
distinct(bank, education) %>% mutate(dummy = 1)
```

# Filter

```{r}
filter(balance == min(balance) | balance == max(balance))

sum(ifelse(balance < 500, 1, 0))
sum(balance < 500)

sum(ifelse(balance < 500, 0, 1))
sum(balance >= 500)
```


```{r}
group_by(bank, age_group = ntile(age,4)) %>%
  summarise(mean_balance = mean(balance), sd_balance = sd(balance)) %>%
  mutate( x = sd_balance / mean_balance)
```

## Exercise 1

```{r}
df <- tibble(dt = c("2019-10-01", "2019-31-12",
                    "2019-03-17", "2019-02-29",
                    "2019-09-30"))
df %>%
  mutate(try_dt = as.Date(dt)) %>%
  filter(is.na(try_dt)) %>%
  .$dt
```

## Exercise 2

```{r}
df_sum1 <- bank %>% group_by(job, education) %>%
  summarise(`mean(Age)` = mean(age, na.rm=TRUE),
            `mean(Balance)` = mean(balance, na.rm=TRUE))

df_sum2 <- bank %>% group_by(job, education="+") %>%
  summarise(`mean(Age)` = mean(age, na.rm=TRUE),
            `mean(Balance)` = mean(balance, na.rm=TRUE))

df_sum3 <- bank %>% group_by(job = "+", education="+") %>%
  summarise(`mean(Age)` = mean(age, na.rm=TRUE),
            `mean(Balance)` = mean(balance, na.rm=TRUE))

df_sum3
```

## Exercise 2 - Version tidy-up

```{r}
# Refactoring
mean_age_balance <- function(df) {
  df %>% summarise(`mean(Age)` = mean(age, na.rm=TRUE),
                   `mean(Balance)` = mean(balance, na.rm=TRUE))
}

df_sum1 <- bank %>% group_by(job, education) %>% mean_age_balance
df_sum2 <- bank %>% group_by(job, education = "+") %>% mean_age_balance
df_sum3 <- bank %>% group_by(job = "+", education = "+") %>% mean_age_balance

df_mean_age_balance <- bind_rows(df_sum1, df_sum2, df_sum3)
df_mean_age_balance
```

## Exercise 3

```{r}
library(fOptions)

df <- tibble(type = sample(c("c", "p"), 100, replace = TRUE),
             strike = round(runif(100) * 100, 0),
             underlying = round(runif(100) * 100, 0),
             Time = 1,
             r = 0.01,
             b = 0,
             sigma = 0.3)

df %>% rowwise() %>% mutate(
  price = GBSOption(TypeFlag = type, S = underlying, X = strike,
                    Time = Time, r = r, b = b, sigma = sigma)@price
) %>% ungroup()
```

# bind_rows

```{r}
x <- c()

for (i in 1:10) {
  x <- c(x, i)
}

x <- tibble()
for (i in 1:10) {
  x <- bind_rows(x, tibble(a = 1:i))
}
x
```

# Summarise/summarize are the same function.

```{r}
df1 <- summarise(bank, day = mean(day), balance = mean(balance)) 
df1 <- summarise_if(bank, is.numeric, mean)
df1
tail(bind_rows(bank,df1),1)
# select(bank, starts_with("p"))
```

```{r}
bank
ncol(bank) * nrow(bank)
```

```{r}
# from slide 45
wfmt <- tibble(date = seq(from = as.Date("2019-01-01"),by = "day",length.out = 5),
Copper_qty = round(runif(5) * 1000, 0),
Gold_qty = round(runif(5) * 1000, 0),
Silver_qty = round(runif(5) * 1000, 0))

# from slide 49
wfmt %>%
pivot_longer(!date, names_to="key", values_to="value") %>%
group_by(date) %>%
summarize(value1 = sum(value)) %>%
rename(value = value1)%>%
mutate(key = "Total") %>%
pivot_wider(names_from=key, values_from=value) %>%
inner_join(wfmt, ., by = "date")
```

# Use filter to create training set.

```{r}
training_set <- filter(bank,
        row_number() %in% sample(1:nrow(bank), round(nrow(bank)*0.75,0)))

# refactoring 1
training_set <- bank %>% filter(.,
        row_number() %in% sample(1:nrow(.), round(nrow(.)*0.75,0)))

# refactor 2
training_select <- function(df, perc=0.75) {
  df %>% filter(.,
        row_number() %in% sample(1:nrow(.), round(nrow(.)*perc,0)))
}

bank %>% training_select()
```

## observe for the change done after group_by

```{r}
str(bank %>% group_by(age) %>% group_by(job))
str(bank %>% group_by(age, job))

```