---
title: "FE8828 Assignment for Exploratory Data Analysis"
author: "Bai Haoyu G1900411H"
date: " 30 Sep 2019"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(bizdays)
# Use echo = TRUE for assignment is an exception, so code is visible.
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

# Finding #1
This data contains `r nrow(bank)` rows and `r ncol(bank)` columns.

# Finding #2
The number of customers in each job group
<p>
Managment and blue-collar are the two biggest groups
```{r Finding 2, echo = TRUE}
jobgroup <- group_by(bank, job)
summary <- summarise(jobgroup, num = n())
summary
```

# Finding #3
The average ages of the customers in each job group
<p>
Surprisingly, people on average loose their jobs in early 40's (so sad)
```{r Finding 3, echo = TRUE}
jobgroup <- group_by(bank, job)
summarise(jobgroup, avg_age = mean(age))
```

# Finding #4
The number of customers in each age group?
<p>
30's and 40's are the two biggest groups
```{r Finding 4, echo = TRUE}
bank_f4 <- mutate(bank, age_group = (age %/% 10) * 10)
agegroup <- group_by(bank_f4, age_group)
summarise(agegroup, num = n())
```

# Finding #5
Plot the number of unemployeed customer in each age group and print the unemployment rate:
<p>
Besides 20's (students), 40's have the highest unemployed rate, which is consistent with finding #3
```{r Finding 5, echo = TRUE}
bank_f4 <- mutate(bank, age_group = (age %/% 10) * 10)
agegroup <- group_by(bank_f4, age_group)
agegroup_num <- summarise(agegroup, total = n())

unemployed_age_group <- dplyr::filter(agegroup, job == "unemployed")
grouped_unemployed_age_group <- group_by(unemployed_age_group, age_group)
unemployed_num <- summarise(grouped_unemployed_age_group, unemployed=n())

unemployed_age <- left_join(unemployed_num, agegroup_num, by = "age_group")
unemployed_rate <- mutate(unemployed_age, rate = unemployed/total)

plot(unemployed_num)
unemployed_rate
```

# Finding #6
The number of customer and their avergae balance in each education group?
<p>
Looks like the highest education group (tertiary) has the highes balance, but primary group has higher balance than secondary group.
One possible explanation is people with only primary education started work ealier and have accumulated more money
```{r Finding 6, echo = TRUE}
educationgroup <- group_by(bank, education)
education_num <- summarise(educationgroup, num = n())
education_balance <- summarise(educationgroup, avg_balance = mean(balance))
education_summary <- left_join(education_num, education_balance, by = "education")

education_summary
```

# Finding #7
Which education group has the most number of married customer?
<p>
Secondary education has the most number of married customers.
```{r Finding 7, echo = TRUE}
educationgroup <- group_by(bank, education)
married_education <- dplyr::filter(educationgroup, marital == "married")
married_num <- summarize(married_education, married=n()) 
married_num <- arrange(married_num, desc(married))
married_num
```

# Finding #8
Which job group has the most number of married customer?
<p>
Surprisingly, there are 10 married students...
```{r Finding 8, echo = TRUE}
jobgroup <- group_by(bank, job)
married_job <- dplyr::filter(jobgroup, marital == "married")
married_num <- summarize(married_job, married=n()) 
married_num <- arrange(married_num, desc(married))
married_num
```

# Finding #9
Interesting Fact 1: having a house or a higher balance does not significantly increase the chance of getting married
```{r Finding 9, echo = TRUE}
maritalgroup <- group_by(bank, marital)
marital_num <- summarise(maritalgroup, total = n())
marital_housing <- dplyr::filter(maritalgroup, housing == "yes")
housing_num <- summarise(marital_housing, with_housing = n())
marital_balance <- summarize(maritalgroup, avg_balance=mean(balance)) 
marital_summary <- left_join(marital_num, housing_num, by = "marital")
marital_summary <- left_join(marital_summary, marital_balance, by = "marital")

marital_summary
```

# Finding #10
Interesting Fact 2: customers in Age group 40 has the highest ratio of negative balance, which is consistent with ealier findings (midlife crisis?)
```{r Finding 10, echo = TRUE}
bank_f4 <- mutate(bank, age_group = (age %/% 10) * 10)
agegroup <- group_by(bank_f4, age_group)
agegroup_num <- summarise(agegroup, total = n())

negative_age_group <- dplyr::filter(agegroup, balance < 0)
grouped_negative_age_group <- group_by(negative_age_group, age_group)
negative_num <- summarise(grouped_negative_age_group, negative_total=n())

negative_age <- left_join(negative_num, agegroup_num, by = "age_group")
negative_rate <- mutate(negative_age, ratio = negative_total/total)
negative_rate <- arrange(negative_rate, desc(ratio))

negative_rate
```




