---
title: "FE8828 Assignment for Exploratory Data Analysis"
author: "XU Han <sub> <Email:xuha0011@e.ntu.edu.sg> </sub>"
date: "Oct 2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(bizdays)
library(dplyr)
library(readr)
library(knitr)
# Use echo = TRUE for assignment is an exception, so code is visible.
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

# Finding #1
```{r}
#compare the average balance among education group
df <- group_by(bank,education) %>% summarise(balance_mean = mean(balance))
kable(df)
```

Among all the education type, the average balance of **tertiary** is highest and the average balance of **secondary** is lowest.

# Finding #2
```{r}
#compare the the percentage of balance>500 between marital group
df2 <- group_by(bank, marital) %>%
  summarise(`balance > 500` = sum(balance > 500),all_count = n(),percentage=`balance > 500`/all_count)
kable(df2)
```

For three marital group, the percentage of balance greater than 500 do not vary a lot.

# Finding #3
```{r}
#Find the job type with highest percentage of housing loan
df3 <- group_by(bank, job) %>%
  summarise(housing_count = sum(ifelse(housing == "no", 0, 1)),count =n(),
            percentage=housing_count/count)%>%filter(percentage==max(percentage)) %>% .$job
df3
```
**Blue-collar** have highest percentage of housing loan among all the job type.

# Finding #4
```{r}
#compare the average duration among different kinds of contact ways
d1 <- filter(bank, contact == "cellular") %>%
  summarize(duration = mean(duration)) %>%
  rename(`Average Duration of Cellular` = duration)
d2 <- filter(bank, contact == "unknown") %>%
  summarize(duration = mean(duration)) %>%
  rename(`Average Duration of Unknown` = duration)
d3 <- filter(bank, contact == "telephone") %>%
  summarize(duration = mean(duration)) %>%
  rename(`Average Duration of Telephone` = duration)
df4 <- bind_cols(d1, d2, d3)
kable(df4)
```

The **unknown and cellular** have almost **same** average duration, and the duration of **telephone** is **lower** than other two.

# Finding #5
```{r}
#Show the number of people with loan among all the job type
df5 <- group_by(bank, job) %>% 
  summarize(loan_y = sum(ifelse(loan =="yes", 1, 0)))
kable(df5)
```


# Finding #6
```{r}
#The number of people over the age of 30 who are still single among all age group
df6=group_by(bank,age) %>% filter(age>30) %>%
  summarise('the number of single'=sum(marital=="single"))
plot(df6$age,df6$`the number of single`,main="the number of single(age>30)",xlab="age(>30)",ylab="number")
```

# Finding #7
```{r}
#The average duration for different age group
df7=group_by(bank,age) %>% summarise(mean_duration=mean(duration))
plot(df7$age,df7$mean_duration,xlab="age",ylab="mean_duration",main="The average duration for different age group")
```

# Finding #8
```{r}
#The number of clients who has a loan while doesn’t have a housing for different education group
df8=group_by(bank,education) %>% filter(loan=="yes",housing=="no") %>% summarise(count=n())
kable(df8)
```

# Finding #9
```{r}
#The number of people whose age is between 20 and 40 for every job type
df9=group_by(bank,job) %>% filter((age>20)|(age<40)) %>% summarise(count=n())
kable(df8)
```

# Finding #10
```{r}
#Compare the average duration for different month
df10=group_by(bank,month) %>% summarise(mean_duration=mean(duration))
plot(df10$month,df10$mean_duration,xlab="month",ylab="mean of duration",main="Average Duration for Different Month")
```
