---
title: "Part 3: Backtest on One-Year Data"
author: "WangPeng, Qu Mengyuan"
date: "2019/10/16"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(fOptions)
library(xts)
library(matrixStats)
knitr::opts_chunk$set(echo = TRUE)
vol<- read_excel("~/Desktop/NTU/PROGRAMMING WEB APPLICATIONS IN FINANCE/FE8828-Qu Mengyuan/group project/Q3/VXAZNCLS.xlsx", 
                 col_types = c("date", "numeric"))
close <- read_excel("~/Desktop/NTU/PROGRAMMING WEB APPLICATIONS IN FINANCE/FE8828-Qu Mengyuan/group project/Q3/VXAZNCLS.xlsx", 
                    sheet = "Sheet2", col_types = c("date", "numeric"))
```

# 1 Output of Backtest 
```{r}
df <- left_join(close,vol,by = c("Date"="observation_date"))
df <- mutate(df, month = as.numeric(substring(df$Date,6,7)))
max_drawdown <- rep(0,12)
sharpe_ratio <- rep(0,12)
final_Pnl <- rep(0,12)
maturity_date <- c()
type <- c("c","c","p","c","c","p","c","c","c","p","p","p")
df1 <- dplyr::filter(df, month == 0)
realized_vol <- rep(0,12)
implied_vol <-rep(0,12)
for(ii in 1:12){
  df_sub <- dplyr::filter(df, month == ii)
  start_date <- min(df_sub$Date)
  end_date <- max(df_sub$Date)
  maturity_date <- c(maturity_date, as.Date(end_date))
  start_price <- df_sub$Close[1]
  df_sub <- mutate(df_sub,volatility = VXAZNCLS/100)
  start_volatility <- df_sub$volatility[1]
  implied_vol[ii] <- start_volatility 
  df_sub <- mutate(df_sub,time_to_M = as.numeric(difftime(as.POSIXct(end_date), as.POSIXct(df_sub$Date, tz="UTC"), units="days")/365))
  df_sub <-df_sub%>%mutate(premium = 100 * GBSOption(TypeFlag = type[ii],
                                                 S = df_sub$Close,
                                                 X = start_price,
                                                 Time = time_to_M,
                                                 r = 0.8/100, # interest rate
                                                 b = 0,
                                                 sigma = start_volatility)@price)%>%
    mutate(Option_DoD_PnL = ifelse(df_sub$Date == start_date,
                                   # On the 1st date, we count the cost of buying the option
                                   premium * (-1),
                                   premium - dplyr::lag(premium))) 
  
  
  df_sub <- df_sub %>%
    rowwise() %>%
    mutate(delta_hedge = 100 * GBSGreeks("delta", TypeFlag = type[ii], S=Close, X = start_price , Time = time_to_M, r = 0.8/100, b = 0, sigma = start_volatility )  * (-1)) %>%
    ungroup()%>%
    mutate(Hedging_DoD_Pnl = ifelse(Date == start_date,
                                    0,
                                    dplyr::lag(delta_hedge) * (Close - dplyr::lag(Close))))
  
  df_sub <- df_sub%>%
    mutate(
           daily_PnL = Option_DoD_PnL + Hedging_DoD_Pnl,
           Option_Final_PnL = cumsum(Option_DoD_PnL),
           Hedging_Final_PnL = cumsum(Hedging_DoD_Pnl),
           Final_PnL = Option_Final_PnL + Hedging_Final_PnL,
           max_d = cummax(Final_PnL) - cummin(Final_PnL),
           portfolio_value = Close * delta_hedge + premium,
           return = ifelse(Date == start_date,
                           0,
                           daily_PnL/dplyr::lag(portfolio_value))
           )
  ln_price <- log(df_sub$Close)/sqrt(1/252)
  
   realized_vol[ii] <- sdDiff(ln_price)
  
  df1 <- bind_rows(df1,df_sub)
  
  final_Pnl[ii] <- df_sub$Final_PnL[nrow(df_sub)]
  max_drawdown[ii] <- 
    {
      xs <- df_sub$Final_PnL
      max(cummax(xs) - cummin(xs))
    }
  
  sharpe_ratio[ii] <- (mean(df_sub$return[2:length(df_sub$return)])-0.008/250)/stdev(df_sub$return[2:length(df_sub$return)])
  
}
backtest <- tibble(Option_Expiry_Date = c(1:12), Sharpe_ratio = sharpe_ratio,
                     Final_PnL = final_Pnl, Max_Drawdown = max_drawdown,
                   Realized_vol = realized_vol, Implied_vol = implied_vol)
backtest
```

# 2 Analysis
## 2.1 Distribution of Final Pnl
### 2.1.1 One trade
The final profit and loss on Option side fluctuates mildly while that on Hedge side changed violently.

In total, the final loss of Delta Hedge Strategy is increased gradually and smoothly.
```{r}
res1 <-dplyr::filter(df1, month == 5)
ggplot(res1,aes(Date,Option_Final_PnL))+geom_col()
ggplot(res1,aes(Date,Hedging_Final_PnL))+geom_col()
ggplot(res1,aes(Date,Final_PnL))+geom_col()
```

### 2.1.2 Backtest
The Final PnL is left skewed, centered around -$6500, which shows that delta hedge strategy can control loss effectively.
```{r}
ggplot(backtest,aes(final_Pnl))+geom_density()
```

## 2.2 Distribution of Max Drawdown
### 2.2.1 One Trade
For one trade, the max drawdown of Delta Hedge Strategy is controled under $1500.

It increases at a decreasing rate as time gets close to maturity.
```{r}
res2 <-dplyr::filter(df1, month == 4)
ggplot(res2,aes(Date,max_d))+geom_col()
```

### 2.2.2 Backtest
The max drawdown is left skewed, controled under $3750, which shows the strategy is robust.
```{r}
ggplot(backtest,aes(max_drawdown))+geom_density()
```

## 2.3 Final Pnl vs Time to maturity
As time to maturity extends, final profit on **Option** side *decreases* while that on **Hedge** side *increases*.

As whole, final loss of delta hedge strategy increases stably as time to maturity reduces and converges to a certain number.
```{r}
res3 <-dplyr::filter(df1, month == 4) 
ggplot(res3, aes(time_to_M,Option_Final_PnL))+geom_point()+geom_smooth()
ggplot(res3, aes(time_to_M,Hedging_Final_PnL))+geom_point()+geom_smooth()
ggplot(res3, aes(time_to_M,Final_PnL))+geom_point()+geom_smooth()
```

## 2.4 Daily Pnl vs Stock Price
Generally, the higher Stock Close Price is, the higher Daily Profit on Option side is while there is no obvious relationship between stock close price and Daily Profit and loss on Hedge side.

As a whole, however, daily profit and loss of delta hedge strategy keeps almost the **same**, which means the strategy can control loss in a reasonable range effectively.
```{r}
res4 <-dplyr::filter(df1, month == 4)
ggplot(res4, aes(Close,Option_DoD_PnL))+geom_point()+geom_smooth()
ggplot(res4, aes(Close,Hedging_DoD_Pnl))+geom_point()+geom_smooth()
ggplot(res4, aes(Close,daily_PnL))+geom_point()+geom_smooth()
```

## 2.5 Sharpe ratio vs Maturity date
There is no direct evidence which indicates a certain relationship between strategy's Sharpe Ratio and time to maturity.

But all sharpe ratios are **positive** with an average of `r mean(sharpe_ratio)`, which indicates the Effectiveness of delta hedge strategy.
```{r}
plot(as.Date(maturity_date), sharpe_ratio)
```

# 2.6 Sharpe ratio vs difference between implied volatility and realized volatility
Generally speaking, ignoring outliers, sharpe ratio is a **linear** function of the square of difference between implied volatility and realized volatility.
```{r}
difference_vol <- (implied_vol - realized_vol)**2
plot(difference_vol,sharpe_ratio)
```




