---
title: "W4A1"
author: "CHEN"
date: "10/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# bank <- read.csv(file = 'bank.csv',sep=";")
```


#Finding 1
People who defaulted has an average balance of around 0.
The age of them ranges from 24-67.
```{r}
ggplot(bank,aes(age,balance,color=default))+geom_point()+geom_smooth()
```

#Finding 2

Management group has the largest proportion of tertiary eduacation while service has the largest proportion of secondary education.

```{r}
ggplot(data = bank, aes(x = job, fill = education)) + 
  geom_bar(binwidth = 10) + 
  theme(text = element_text(size=8))
```

#Finding 3

people who have a loan has a more centralized balance.

```{r}
ggplot(data = bank, aes(loan, balance)) + 
  geom_boxplot() + 
  theme(text = element_text(size=8))
```

#Finding 4

People who had a divorce is older than who are married or single on average.
```{r}
ggplot(data = bank, aes(marital, age)) + 
  geom_boxplot() + 
  theme(text = element_text(size=8))
```

#Finding 5
Management group has a higher proportion of divorce than bule collars.

```{r}
ggplot(data = bank, aes(x = job, fill = marital)) + 
  geom_bar(binwidth = 10) + 
  theme(text = element_text(size=8))
```

#Finding 6
Most people have duration between 0 and 450.
```{r}
 ggplot(data = bank, mapping = aes(x = duration, fill = job)) + geom_histogram(binwidth = 100) + theme(text = element_text(size=8))
```