
title: "FE8828 Assignment for Exploratory Data Analysis"
author: "Yao Yang <sub> <Email:teoyaoyang@gmail.com> </sub>"
date: "Oct 2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(bizdays)
library(ggplot2)
library(kableExtra)

# Use echo = TRUE for assignment is an exception, so code is visible.
knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)
bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

# Finding #1 - There is a wide variation of mean age (as well as distribution) across the various jobs. Unsurprisingly, Retirees have the highest mean age, while students have the lowest.
```{r}
ggplot(bank, aes(reorder(job, -age), age)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Finding #2 - Younger customers tend to prefer using cellular as the mode of contact
```{r}
# Find the big age group
ggplot(bank, aes(age, color = contact, alpha = 0.3)) +geom_density()
```

# Finding #3 - Considerable variation in the education levels in various jobs. Management seems to be most highly educated, while admin seems to be most lowly education.
```{r}
ggplot(data = bank, aes(x = job, fill = education)) + geom_bar(position="fill") +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Finding #4 - balance generally increases with age, as the regression line is upward sloping
```{r}
ggplot(bank, aes(age,balance)) + geom_point(aes(color=factor(job))) + geom_smooth(method="lm") + ylim(0,30000)

```

# Finding #5 - there doesn't seem to be any discernible relationship between education and our response variable
```{r}
ggplot(bank, aes(education, y)) + geom_jitter()
```

# Finding #6 - there's considerable seasonality in the data, with a lot of data from May
```{r}
ggplot(bank, aes(x=factor(1), fill=month))+
  geom_bar(width = 1)+
  coord_polar("y")

```

