---
title: "Exploratory Data Analysis"
author: "Tan Mengting"
date: "2020/10/9"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(lubridate)
library(bizdays)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE, fig.align="center", collapse = TRUE, cache = TRUE)

# bank <- read.csv("https://goo.gl/PBQnBt", sep = ";")
```

## R Markdown
# Finding #1
## Discover insights of age distribution, relationship with crdit and mean balance
* Survey participants are mostly composed of young and middle-aged people
* 60-70 group has **smaller size** but **larger balance mean**, but the eldest group has a lower balance mean.
* Peopel below 50 tend to have more credit, but the total credit ownership rate is very low(max  4%).
* The youngest and oldest group tend to have higher subscription rate.
* People of middle age have the largest subscription size but the rate is the lowest.
```{r}

group_by(bank, age) %>%
  summarise(count = n(), 
            balance_mean = mean(balance), 
            default_count = sum(ifelse(default == "no", 0, 1)),
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "default_rate(%)" = default_count/count*100,
            "subscription_rate(%)" = subscription_count/count*100) %>%
  arrange(age) -> res
res
res %>% plot

```

# Finding #2
## Discover insights of job and age
* Only students and retired people have obvious age bias.
```{r}
ggplot(bank, aes(job, age)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle=90, hjust=1))
```

# Finding #3
## Discover insights of job distribution, relationship with balance mean, default rate and subscription rate
* Many more people take blue0collar and management work.
* Retired people have highest mean balance.
* Blue-collar, unemployed and services people have lowest mean balance.
```{r}
group_by(bank, job) %>%
  summarise(count = n(), 
            balance_mean = mean(balance), 
            default_count = sum(ifelse(default == "no", 0, 1)),
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "default_rate(%)" = round(default_count/count*100,2),
            "subscription_rate(%)" = round(subscription_count/count*100,2)) %>%
  arrange(job) -> res
res

ggplot(res, aes(job, count, fill=job))  +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme(axis.text.x = element_text(angle=90, hjust=1))

ggplot(res, aes(job, balance_mean, fill=job))  +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme(axis.text.x = element_text(angle=90, hjust=1))
```

# Finding #4 
## Discover insights of education and job
* Primary education leads to most blue-collar jobs.
* Secondary education leads to most admin, blue-collar, services and technician jobs.
* Tertiary educaiton leads to most	management jobs, and these prople contributed to the largest total balance.
```{r}
group_by(bank, education,job) %>%
  summarise(count = n(), 
            balance_mean = mean(balance),
            balance_sum = sum(balance),
            default_count = sum(ifelse(default == "no", 0, 1)),
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "default_rate(%)" = default_count/count*100,
            "subscription_rate(%)" = subscription_count/count*100) %>%
  arrange(education) -> res
res

```

# Finding #5 
## Discover insights of housing loan
* People with no housing loans tend to be elder, have more balance and double the subscription rate than those with housing loans
```{r}
group_by(bank, housing) %>%
  summarise(count = n(), 
            balance_mean = mean(balance), 
            age_mean = mean(age), 
            default_count = sum(ifelse(default == "no", 0, 1)),
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "default_rate(%)" = default_count/count*100,
            "subscription_rate(%)" = subscription_count/count*100) %>%
  arrange(housing) -> res
res
```


# Finding #6
## Discover insights of contact and type
* Contacts through teltphone tend to have shorter duration but almost same subscription rate as cellular contact and much higher than unknown contact
```{r}

ggplot(bank, aes(contact, duration)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle=90, hjust=1))

group_by(bank, contact) %>%
  summarise(count = n(), 
            balance_mean = mean(balance), 
            duration_mean = mean(duration),
            default_count = sum(ifelse(default == "no", 0, 1)),
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "default_rate(%)" = default_count/count*100,
            "subscription_rate(%)" = subscription_count/count*100) %>%
  arrange(contact) -> res
res


```


# Finding #7
## Discover insights of last contact month
* People who last contacted in May tend to have the highest subscription rate and also the largest subscription number
```{r}

bank %>%
  group_by(month,y) %>%
  summarise(count = n()) %>%
  arrange(month) -> res
res

ggplot(res, aes(month, count, fill=y)) +
  geom_bar(stat = 'identity', position = 'dodge') 


group_by(bank, month) %>%
  summarise(count = n(), 
            subscription_count = sum(ifelse(y == "no", 0, 1)),
            "subscription_rate(%)" = round(subscription_count/count*100,2)) %>%
  arrange(month) -> res
res

ggplot(res, aes(month, count))  +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme(axis.text.x = element_text(angle=90, hjust=1))
```