---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: Yang Ye
institute: Nanyang Business School
# titlegraphic: /Dropbox/teaching/clemson-academic.png
fontsize: 10pt
output:
 beamer_presentation:
    template: ./latex-beamer.tex
    # keep_tex: true
    latex_engine: xelatex # pdflatex also works here
    dev: cairo_pdf # I typically comment this out if latex_engine: pdflatex
    slide_level: 3
    # theme: "metropolis"
make149: false
classoption: "aspectratio=169"
mainfont: "Bera Sans" # Open Sans
titlefont: Calibri # Try out some font options if xelatex
sansfont: "FiraCode NF" # Bera Sans Mono
monofont: "Bera Sans Mono" # FiraCode NF
header-includes:
# - \usecolortheme[snowy]{owl}
- \usetheme{default}
- \beamertemplatenavigationsymbolsempty
---

```{r setup2, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.path='figs/')
knitr::opts_chunk$set(cache.path='cache/')
knitr::opts_chunk$set(
                  fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      }
                  )
library(tidyverse)
# library(stevemisc)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

ABC

    a <- 1
    print(a)


    a <- 1
    print(a)


DDD


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

